\LARGE Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-10-08 poster/main.tex
update plots

@@

\addtobeamertemplate{block end}{}{\vspace*{2ex}} % White space under blocks

\begin{frame}[t] % The whole poster is enclosed in one beamer frame

@@

\begin{column}{.02\textwidth}\end{column} % Empty spacer column

\begin{column}{.465\textwidth} % The first column

@@

\begin{block}{Objectives}
\noindent Design a mechanism that achieve differential privacy by scaling to a metric between distribution.
\begin{enumerate}
\item A differentially private bayesian mechanism,
\item Calibrating mechanism noise by the same probabilistic distance we want to measure accuracy with.
\item Applying smooth sensitivity in mechanism to achieve better accuracy.
\end{enumerate}

@@

\begin{block}{Bayesian Inference Background}
% The first subdivided column within the first main column
% \begin{columns} % Subdivide the first main column
% \begin{column}{.54\textwidth} % The first subdivided column within the first main column
beta
distribution, $\betad(\alpha, \beta)$, with parameters
$\alpha,\beta\in\mathbb{R}^{+}$, and with p.d.f:

\[
  \Pr(\theta)\equiv \frac{\theta^{\alpha} (1- \theta)^{\beta}}{\betaf(\alpha,\beta)}
\]
where $\betaf(\cdot,\cdot)$ is the beta function.
The data $\dataobs$ will be a sequence of $n\in\mathbb{N}$ binary values, that is $\dataobs= (x_1,\dots x_n), x_i\in\{0,1\}$, and the likelihood function is:
\[
  \Pr(\dataobs | \theta)\equiv \theta^{\Delta \alpha}(1-\theta)^{n - \Delta \alpha}
\]
where $\Delta \alpha = \displaystyle\sum_{i=1}^{n}x_i$.
From this it can easily be derived that the posterior distribution is:
\[
  \Pr(\theta|\dataobs)=\betad(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)
\]
\end{block}

%----------------------------------------------------------------------------------------
%	MATERIALS
%----------------------------------------------------------------------------------------

\begin{block}{Differentially private Bayesian inference}
% We are interested in the 
% situation where: we have some  private data $\vec{x}$, some public data
% $\vec{y}$, a set of parameter $\theta$, and a public prior $p(\theta)$
% on $\theta$. We want to compute the public posterior distribution $p(\theta\
% |\ \vec{x}, \vec{y})$ in a differentially private way. This
% corresponds to make sure that
% for given values $\epsilon$ and $\delta$, and for every $\vec{x}$ and $\vec{x'}$ 
% differing in one element we have
Release a private version of posterior distribution $(\tilde\alpha,\tilde\beta)=(\alpha +  \widetilde{\Delta \alpha},\beta + n - \widetilde{\Delta \alpha})$
where $\widetilde{\Delta \alpha}\sim Lap(\Delta \alpha, \frac{2}{\epsilon})$,
and where $Lap(\mu,\nu)$ denotes a Laplace random variable with mean $\mu$ and scale $\nu$.

@@

\begin{block}{Our Approach - Exponential Mechanism with Smooth Sensitivity}

define the mechanism $\hexpmech$ which, given in input a
sequence of observations $\dataobs$ and parameters $\epsilon>0$ and
$\delta>0$, produces an element $r$ in $\betaset$ with probability:

\begin{equation*}
\underset{z \thicksim \hexpmech}{\Pr}[z=r] = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}
{\displaystyle\sum_{r\in\betaset} exp\Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\Big)}.
\end{equation*}

The smooth sensitivity is
computed as follows:
\begin{equation}
  \label{eq:smooth}
   S(\dataobs)=\max_{\dataobs' \in \{0,1\}^{n}}\bigg \{\Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )\cdot e^{-\gamma\cdot d(C(\dataobs), C(\dataobs'))}\bigg\},
\end{equation}
where $d$ is the Hamming distance between two datasets,
$\gamma =
\gamma(\epsilon, \delta)$ is a function of $\epsilon$ and $\delta$ to
be determined later, and where $\Delta_{l}\bigg
(\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )$ denotes the local
sensitivity at $\bysinfer(\dataobs')$, or equivalently at $\dataobs'$,
of the scoring function used in our mechanism. That is:
\begin{equation*}
\Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )=\max_{\dataobs'' \in \datauni^n:\adj{\dataobs'}{\dataobs''}, r\in \betaset}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs''), r)\rvert.
\end{equation*}

@@

\begin{column}{.03\textwidth}\end{column} % Empty spacer column

\begin{column}{.465\textwidth} % The second column

@@

\begin{block}{Conclusion and Future Work}

@@

  \item 
  \begin{enumerate}
    \item  The accuracy that we are going to explore next, and in a more principled and formal way.

    \item  Experiments have shown that the actual privacy loss
  in the experiments can be smaller than $\epsilon$. This means that we
  could improve accuracy, by adding less noise but still achieve
  $(\epsilon, \delta)$-dp.

    \item The choice of the Hellinger distance might seem quite ad-hoc. Hence, it is worth exploring other distances over distributions. An interesting class of probability metrics is the family of $f$-divergences \cite{CIT-004}.

    \item Other application of our scheme are going to be explored.
  \end{enumerate}
\end{itemize}
%\vspace{8mm}
%\vspace{8mm}
%where we require $t$ and $u$ to have distinct sets of free variables.
\end{block}

@@

>>>>

\setbeamercolor{background canvas}{bg=white!20}

@@

\addtobeamertemplate{block end}{}{\vspace*{1ex}} % White space under blocks
\begin{frame}[t] % The whole poster is enclosed in one beamer frame

@@

\begin{column}{.485\textwidth} % The first column

@@

\begin{block}{Objectives}
\begin{columns} % Subdivide the first main column
\begin{column}{.6\textwidth}
\noindent Design a mechanism that achieve differential privacy by scaling to a metric between distribution.
\begin{enumerate}
\item A differentially private bayesian mechanism,
\item Calibrating mechanism noise by the same probabilistic distance we want to measure accuracy with.
\item Applying smooth sensitivity in mechanism to achieve better accuracy.
\end{enumerate}
\end{column}
\begin{column}{.4\textwidth}
\begin{figure}[ht]
\centering
\includegraphics[width=0.5\textwidth]{poster_0.eps}
\caption{Hellinger Sensitivity}
\label{fig_sensitivity}
\end{figure}
% \vspace{.1cm}
\end{column}
\end{columns}

% \noindent Design a mechanism that achieve differential privacy by scaling to a metric between distribution.
% \begin{enumerate}
% \item A differentially private bayesian mechanism,
% \item Calibrating mechanism noise by the same probabilistic distance we want to measure accuracy with.
% \item Applying smooth sensitivity in mechanism to achieve better accuracy.
% \end{enumerate}

@@

\begin{block}{Bayesian Inference Background}
% The first subdivided column within the first main column
% \begin{columns} % Subdivide the first main column
% \begin{column}{.54\textwidth} % The first subdivided column within the first main column
Conjugate prior distribution, $\betad(\alpha, \beta)$, with hyper parameters $\alpha,\beta\in\mathbb{R}^{+}$;

Observed data set $\dataobs$: $\dataobs= (x_1,\dots x_n), x_i\in\{0,1\}$, $n\in\mathbb{N}$

Bernoulli likelihood function:
  $\Pr(\dataobs | \theta)\equiv \theta^{\Delta \alpha}(1-\theta)^{n - \Delta \alpha}$
where $\Delta \alpha = \displaystyle\sum_{i=1}^{n}x_i$;

Posterior distribution derived: 
$\Pr(\theta|\dataobs)=\betad(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)$

\end{block}
% and with p.d.f:

% \[
%   \Pr(\theta)\equiv \frac{\theta^{\alpha} (1- \theta)^{\beta}}{\betaf(\alpha,\beta)}
% \]
% where $\betaf(\cdot,\cdot)$ is the beta function.
%----------------------------------------------------------------------------------------
%	MATERIALS
%----------------------------------------------------------------------------------------

\begin{block}{Differentially private Bayesian inference}
Release a private version of posterior distribution $(\tilde\alpha,\tilde\beta)=(\alpha +  \widetilde{\Delta \alpha},\beta + n - \widetilde{\Delta \alpha})$.

In a baseline approach, we sample noise from $Lap(\mu,\nu)$ mechanism, i.e., $\widetilde{\Delta \alpha}\sim Lap(\Delta \alpha, \frac{2}{\epsilon})$,

@@

\begin{block}{Smoothed Hellinger Distance based Exponential Mechanism}

Our approach defines the mechanism $\hexpmech$: given in input an observations $\dataobs$, parameters $\epsilon>0$ and $\delta>0$, produces an element $r$ in $\betaset$ with probability:
$\underset{z \thicksim \hexpmech}{\Pr}[z=r] = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}
{\displaystyle\sum_{r\in\betaset} exp\Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\Big)}.$

The smooth sensitivity is
computed as follows:
\begin{equation*}
  \label{eq:smooth}
   S(\dataobs)=\max_{\dataobs' \in \{0,1\}^{n}}\bigg \{\Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )\cdot e^{-\gamma\cdot d(C(\dataobs), C(\dataobs'))}\bigg\},
\end{equation*}
where $d$ is the Hamming distance between two datasets,
$\gamma =
\gamma(\epsilon, \delta)$ is a function of $\epsilon$ and $\delta$ to
be determined later, and where $\Delta_{l}\bigg
(\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )$ denotes the local
sensitivity at $\bysinfer(\dataobs')$, or equivalently at $\dataobs'$,
of the scoring function used in our mechanism. That is:
\begin{equation*}
\Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )=\max_{\dataobs'' \in \datauni^n:\adj{\dataobs'}{\dataobs''}, r\in \betaset}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs''), r)\rvert.
\end{equation*}

@@

\begin{column}{.01\textwidth}\end{column} % Empty spacer column

\begin{column}{.485\textwidth} % The second column

@@

\begin{block}{Conclusion}

@@

  \item 
  % \begin{enumerate}
  %   \item  The accuracy that we are going to explore next, and in a more principled and formal way.

  %   \item  Experiments have shown that the actual privacy loss
  % in the experiments can be smaller than $\epsilon$. This means that we
  % could improve accuracy, by adding less noise but still achieve
  % $(\epsilon, \delta)$-dp.

  %   \item The choice of the Hellinger distance might seem quite ad-hoc. Hence, it is worth exploring other distances over distributions. An interesting class of probability metrics is the family of $f$-divergences \cite{CIT-004}.

  %   \item Other application of our scheme are going to be explored.
  % \end{enumerate}
\end{itemize}
%\vspace{8mm}
%\vspace{8mm}
%where we require $t$ and $u$ to have distinct sets of free variables.
\end{block}

@@

\begin{column}{.01\textwidth}\end{column} % Empty spacer column
